---
title: My dynamic report
output: html_fragment
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE,
                      fig.width=6, fig.height=4, out.width = "100%")
library(tidyverse)
```

```{css}
@import url('https://fonts.googleapis.com/css2?family=Oldenburg&display=swap');

body {
  background-color: #F5F5F5;
  font-family: 'Oldenburg', sans-serif;
  font-size: 18px;
  margin: 0;
  padding: 0;
}

h2 {
  font-size: 3em;
  text-align: center;
  margin-bottom: 1em;
  max-width: 50%;
  min-width: 800px; 
  margin: 0 auto;
  padding: 20px;
}

h3 {
  font-size: 2em;
  text-align: center;
  margin-bottom: 1em;
  max-width: 50%;
  min-width: 800px; 
  margin: 0 auto;
  padding: 20px;
}

p {
  max-width: 50%;
  min-width: 800px; 
  margin: 0 auto;
  padding: 20px;
  border-radius: 18px;
  text-align: left;
  line-height: 1.6; 
  border-bottom: 3px solid #A7C7E7;
  border-right: 3px solid #A7C7E7;
}

strong {
  color: #4A90E2; 
}
```

## Hydration Patterns and Environmental Influences

This report explores hydration behaviour across different individual and the environmental factors associated. We analyse how factors such as age, time of day, temperature, humidity, physical activity and beverage type influence water intake. \
\
The data was collected via an observational survey where participants recorded their water/beverage consumption at various points during the day. \
\
Each submission captures the amount consumed, perceived thirst and environmental conditions at the time of the observation. The goal is to understand patterns in water intake and identify key factors that affect hydration behaviour.

```{r include=FALSE}

logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vT7Ei4Z4JJvaZLsHuqcYsvymgKPFKHdxElqiKDeH7ZNFCTwzdbB2YWSDpmE5BFXuJSx0lyraGFZUtly/pub?gid=139541697&single=true&output=csv")

latest_data <- logged_data %>%
  rename(timestamp = 1,
         first_time = 2,
         age_group = 3,
         hour = 4,
         humidity = 5,
         physical_activity = 6,
         quantity_ml = 7,
         is_water = 8,
         temperature = 9,
         thirst_level = 10)

latest_data$is_water <- ifelse(
  latest_data$is_water == "Yes", "Water", "Non-water drink")

latest_data$first_time <- factor(latest_data$first_time)
latest_data$age_group <- factor(latest_data$age_group)
latest_data$hour <- factor(latest_data$hour)
latest_data$humidity <- factor(latest_data$humidity)
latest_data$physical_activity <- factor(latest_data$physical_activity)
latest_data$is_water <- factor(latest_data$is_water)
latest_data$temperature <- factor(latest_data$temperature)

latest_data$age_group <- factor(latest_data$age_group, 
                                  levels = c("Under 18", "18-25", "26-40", 
                                             "40+"), 
                                  ordered = TRUE)

latest_data$temperature <- factor(latest_data$temperature, 
                                  levels = c("Very cold", "Cold", "Comfortable", 
                                             "Warm", "Hot", "Very hot"), 
                                  ordered = TRUE)

num_observations <- length(latest_data$timestamp)

num_respondents <- sum(latest_data$first_time == "Yes")

avg_response <- (num_observations / num_respondents) %>%
  round(1)

max_quantity <- max(latest_data$quantity_ml)

median_quantity <- median(latest_data$quantity_ml) %>%
  round(2)

mean_thirst <- mean(latest_data$thirst_level) %>%
  round(1)

```

In total, **`r num_observations`** water or beverage intake records were logged during the survey. These observations came from **`r num_respondents`** participants, each submitting an average of **`r avg_response`** observations. \
\
The median reported water intake was **`r median_quantity`** ml, with the maximum intake being **`r max_quantity`** ml. On average, participants rated their thirst as **`r mean_thirst`** on a 1 (very hydrated) to 5 (very dehydrated) scale.

### Observations by Age Group, Time of Day and Temperature

```{r, echo= F}
age_group_plot <- latest_data %>%
  ggplot() +
    geom_bar(aes(x = age_group), 
             fill = "#CDB4DB") +
  theme_minimal() +
  labs(title = "Observations by Age Group",
       x = "Age Group",
       y = "Number of Drinking Events")

age_group_plot
```

```{r, echo= F}
hour_plot <- latest_data %>%
  ggplot() +
  geom_bar(aes(x = hour), 
           fill = "#A7C7E7") +
  theme_minimal() +
  labs(title = "Observations by Time of Day",
       x = "Time of Day",
       y = "Number of Drinking Events")

hour_plot
```

```{r, echo= F}
temperature_plot <- latest_data %>%
  ggplot() +
  geom_bar(aes(x = temperature), 
           fill = "#78DAAE") +
  theme_minimal() +
  labs(title = "Observations by Perceived Temperature",
       x = "Perceived Temperature",
       y = "Number of Drinking Events")

temperature_plot
```
